Letter: Performance models for \\ high-resolution ice sheet simulations

### 2022-06-22 paper/perfmod.tex
an abstract

\abstract{\today. FIXME}

>>>>

\abstract{Modern numerical ice sheet models, with horizontal resolutions of a few kilometers or less, compute evolving ice geometry and velocity fields using various widely-discussed stress-balance approximations and boundary conditions.  The practical performance of such numerical models is, however, often dominated by stability conditions for currently-standard explicit time-stepping.  (Current schemes generally update ice thickness after a velocity solution.)  Such models take many short, stability-limited time steps.  In this note, performance of numerical models is clarified by quantifying computational effort, in the asymptotic limit of many map-plane mesh nodes, in terms of major computational parameters.  The potential of coming generations of Stokes dynamics and/or implicit time-stepping numerical models is assessed.}
